model4you reproducing: Individual treatment effect prediction for amyotrophic lateral sclerosis patients

### 2018-01-08 pkg/model4you/inst/reproducing_papers/2017_individual_treatment_effect_als_smmr.Rmd
reproducing papers
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1927 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0a30edddd44a1d218ade492fa1d92b42bb06195c

---
title: model4you reproducing "Individual treatment effect prediction for amyotrophic
  lateral sclerosis patients"
author: "Heidi Seibold"
date: "December 22, 2017"
output: html_document
---

>>>>

---
title: "model4you reproducing: Individual treatment effect prediction for amyotrophic lateral sclerosis patients"
author: "Heidi Seibold"
date: "December 22, 2017"
output: html_document
---
